% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Xiaocong (Cecilia) Lv}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Faculty of Transportation Engineering,Central South University}
 \moveleft.5\hoffset\centerline{CHANGSHA,HUNAN 410075 China}
 \moveleft.5\hoffset\centerline{(+86)18890059915}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\begin{resume}
 
 

\section{EDUCATION} \textbf {CENTRAL SOUTH UNIVERSITY(CSU),China}  \hfill{2017.09-pres}\\
                    \textbf{ MSc in Transportation Equipment \& Control Engineering} \hfill{}\\
                \textbf {\textit {Thesis Focus:}}  Image Processing, Deep Learning ,Computer Vision \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                {\sl Coursework:} Artificial Neural Network, Intelligent detection and signal processing, Vehicle system dynamics, Computational fluid dynamics foundation, Scientific Paper Writing.
                
                \textbf {Wuhan University of Science and Technology,China}  \hfill{2013.09-2017.06}\\
                    \textbf{ Diploma in Traffic \& Transportation } \hfill{GPA:3.29/4}\\
                \textbf {\textit {Graduation thesis:}}  Asphalt Pavement Texture Extraction Based on Digital Image Processing\\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                {\sl Coursework:} Traffic Engineering,Mechanical Drawing,Engineering MEchanics, TransCAD, Mechanical Design Basis, Traffic Geographic Information System, Traffic Safety Theory.
 

 
\section{EXPERIENCE} \textbf { CSU, Dept. of Transportation Engineering   } \hfill 2017.09-pres \\
\textbf {Researcher , CAD/CAM Research Laboratory}
               
                 \begin{itemize}  
                 \itemsep -2pt %reduce space between items
                 \item  Finished Image distortion correction and stitching based on MATLAB.
                \item   Studeyed about Panorama 360 AVM system.
                \item   Participated the project of "Diversified Technologies for Guided Transport System Models".
                \item   Participated the project of "TEDS system based on Deep Learning"
                \end{itemize}
 \textbf { Wuhan University of Science and Technology, \\Dept. of Transportation Engineering   } \hfill 2014.09-2017.06 \\
               \textbf {Awards}
                 \begin{itemize}  
                 \itemsep -2pt %reduce space between items
                 \item  Selected as the outstanding student Per year.
                \item   Awarded the third prize Per year.
                \end{itemize}
               

\section{EXTRA-CURRICULAR \\ ACTIVITIES}   
                 \textbf { Wuhan University of Science and Technology.\\Faculty of Transportation and Vehicle Engineering  }  \hfill{2013.09-2014.06}\\
              \begin{itemize}  
                 \item Member of Young Volunteers Association
                 \item Member of  Outreach Department of Student Union
                 \end{itemize} 
                  
            
                
\section{ SKILLS }  \textbf {\textit {Computer:}}\\  
 {\sl Engineering:}  \ \ MATLAB\\ 
 {\sl Programming:} C\\
 {\sl Other:} \ \ \ \ \ \ \ \ \ \ Adobe Photoshop, Latex,  Linux, Win, Office\\
    \textbf {\textit {Language:}} \\ English, Chinese\\

      
                 
 

\end{resume}
\end{document}




